WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2014-06-02 ms.tex
Oops, add subscript
Minor edits

Assuming circular orbits and no spin precession, we can write the \ac{GW} signal in each detector as a linear combination of two basis waveforms $h_0$ = $h$ and $h_{\pi/2}$. For nonprecessing systems, $h_0$ and $h_{\pi/2}$ are approximately ``in quadrature'' in the same sense as the sine and cosine functions, being nearly orthogonal and out of phase by ${\pi/2}$ at all frequencies. If $h_0$ and $h_{\pi/2}$ are Fourier transforms of real functions, then $h_0(\omega) = h_0^*(-\omega)$ and $h_{\pi/2}(\omega) = h_{\pi/2}^*(-\omega)$, and we can write (assuming an arbitrary phase convention)
%
\begin{equation}
	h_{\pi/2}(\omega) = h_0(\omega) \cdot
	\cases{
		-i & if $\omega \geq 0$ \\
		i & if $\omega < 0$
	}.
\end{equation}
%
Then, we can write the signal model in a way that isolates all dependence on the extrinsic parameters $\boldsymbol\theta_\mathrm{ex}$ into the coefficients and all dependence on the intrinsic parameters $\boldsymbol\theta_\mathrm{in}$ into the basis waveform, by taking the Fourier transform of Equation~(2.8) of \cite{PhysRevD.83.084002}:
%
\begin{equation}\label{eq:full-signal-model}
	h_i(\omega; \boldsymbol\theta) = \e^{-i \omega t_\oplus}
	\frac{D_{1,i}}{D_\mathrm{L}}
	\e^{2 i \phi_c}
	\left[
	\frac{1}{2} \left(1 + \cos^2 \iota\right) \Re \left\{z\right\} - i
	\left(\cos\iota\right) \Im z
	\right]
	h(\omega; \boldsymbol\theta_\mathrm{in})
\end{equation}
%
for $\omega \geq 0$, where
%
\begin{equation}
	z = e^{-2 i \psi} \left(
	F_{+,i}(\alpha, \delta, t_\oplus) +
	i F_{\times,i}(\alpha, \delta, t_\oplus)
	\right).
\end{equation}
%
The quantities $F_{+,i}$ and $F_{\times,i}$ are the dimensionless detector antenna factors, and depend on the orientation of detector $i$ as well as the sky location and sidereal time of the event, and are derived in~\cite{PhysRevD.63.042003}. The quantity $D_{1,i}$ is a fiducial distance at which detector $i$ would register SNR=1 for an optimally oriented binary (face\nobreakdashes-on, and in a direction perpendicular to the interferometer's arms),
%
\marginpar{I seem to have dropped a factor of 2 here...}%
%
\begin{equation}\label{eq:horizon}
D_{1,i} = 1 / \sigma_i, \qquad {\sigma_i}^2 = \int_0^\infty \frac{\left|h(\omega; \mathbf \theta)\right|^2}{S_i(\omega)} \,d\omega.
\end{equation}

@@

The Fisher information matrix for a measurement $x$ described by the unknown parameter vector $\boldsymbol{\theta}$ is
%
\begin{equation}\label{eq:general-fisher-matrix}
	\mathcal{I}_{jk} = \mathrm{E} \, \left[
		-\frac{\partial^2 \log
			\mathcal{L}(x_i ; \boldsymbol\theta)}
			{\partial \theta_j \theta_k}
	\middle| \boldsymbol\theta
	\right].
\end{equation}
%
This equation involves double derivatives, but substantial simplification is possible when---as in this case---the likelihood is Gaussian:
%
\begin{equation}\label{eq:gaussian-fisher-matrix}
	\mathcal{I}_{jk} = \int_0^\infty \Re \left[
        \left(\frac{\partial h_i}{\partial \theta_j}\right)^*
        \left(\frac{\partial h_i}{\partial \theta_k}\right)
	\right] \frac{1}{S_i(\omega)} \, d\omega.
\end{equation}
%
This form is more useful because it involves only first derivatives, and of the signal $h (\omega)$ rather than the entire observation $x (\omega)$. In terms of the $k$th \ac{SNR}-weighted moment of angular frequency,
%
\begin{equation}\label{eq:angular-frequency-moments}
    {\overline{\omega^k}}_i =
        \left[ \int_0^\infty \frac{|h (\omega)|^2}{S_i(\omega)} \omega^k \, d\omega \right]
        \left[ \int_0^\infty \frac{|h (\omega)|^2}{S_i(\omega)} \, d\omega \right]^{-1},
\end{equation}
%
the Fisher matrix for the signal in the $i$th detector is
%
\begin{equation}
	\mathcal{I}_i = \left(
		\begin{array}{cc}
			\mathcal{I}_{\boldsymbol\theta_i,\boldsymbol\theta_i} &
			\mathcal{I}_{\boldsymbol\theta_i,\boldsymbol\theta_\mathrm{in}} \\
			{\mathcal{I}_{\boldsymbol\theta_i,\boldsymbol\theta_\mathrm{in}}}^\intercal &
			{\rho_i}^2 \mathcal{I}_{\boldsymbol\theta_\mathrm{in},\boldsymbol\theta_\mathrm{in}}
		\end{array}
	\right)
\end{equation}
%
where
%
\begin{equation}\label{eq:fisher-matrix}
	\mathcal{I}_{\boldsymbol\theta_i,\boldsymbol\theta_i} = \bordermatrix{
        ~ & \rho_i & \gamma_i & \tau_i \cr
        \rho_i & 1 & 0 & 0 \cr
        \gamma_i & 0 & {\rho_i}^2 & -{\rho_i}^2 {\overline{\omega}}_i \cr
        \tau_i & 0 & -{\rho_i}^2 {\overline{\omega}}_i & {\rho_i}^2 {\overline{\omega^2}}_i
    }.
\end{equation}
%
To lowest post\nobreakdashes-Newtonian order, the intrinsic parameters affect the phase evolution but not the amplitude evolution, so for BNS systems we can assume $\mathcal{I}_{\rho_i,\boldsymbol\theta_\mathrm{in}} \approx 0$.
%
\marginpar{Show this?}%
%
When we form the Fisher matrix for the whole network, if the detectors all have the same noise \acp{PSD}, $S_1(\omega) = S_1(\omega) = \cdots = S_n(\omega) \equiv S(\omega)$, then we can change variables from phases and times on arrival $\left\{\gamma_i, \tau_i\right\}_i$ to appropriate differences between them, in order to cancel out all off-diagonal terms between the intrinsic and extrinsic parameters. Because all existing ground-based GW detectors have similar bandpasses, we restrict all of our further attention to just the extrinsic part of the Fisher matrix, $\mathcal{I}_{\boldsymbol\theta_i,\boldsymbol\theta_i}$.

@@

We can compute the Fisher matrix elements for the autocorrelation likelihood given by \Eref{eq:autocor-likelihood}, with detector subscript suppressed:
%
\begin{eqnarray}
	\nonumber
	\mathcal{I}_{\rho\rho} &=& 1 \\
	\nonumber
	\mathcal{I}_{\rho\gamma} &=& 0 \\
	\nonumber
	\mathcal{I}_{\rho\tau} &=& 0 \\
	\label{eq:fisher-autocor-gamma-gamma}
	\mathcal{I}_{\gamma\gamma} &=& \rho^2
		\int_{-T}^T \left|a(t)\right|^2 w(t; \rho) dt \\
	\label{eq:fisher-autocor-tau-tau}
	\mathcal{I}_{\tau\tau} &=& -\rho^2
		\int_{-T}^T \Re\left[a^*(t) a''(t)\right] w(t; \rho) dt \\
	\label{eq:fisher-autocor-gamma-tau}
	\mathcal{I}_{\gamma\tau} &=& -\rho^2
		\int_{-T}^T \Im\left[a^*(t) a'(t)\right] w(t; \rho) dt \\
	\nonumber\textrm{where} && \\
	\nonumber
	a'(t) &=& \frac{\partial a}{\partial t} \\
	\nonumber
	a''(t) &=& \frac{\partial^2 a}{\partial t^2} \\
	\nonumber
	w(t; \rho) &=& \frac{
		\displaystyle
		\exp\left[\frac{\rho^2}{4}\left|a(t)\right|^2\right]
		\left(
		I_0\left[\frac{\rho^2}{4}\left|a(t)\right|^2\right] +
		I_1\left[\frac{\rho^2}{4}\left|a(t)\right|^2\right]
		\right)
	}{
		\displaystyle
		2 \int_{-T}^T
		\exp\left[\frac{\rho^2}{4}\left|a(t')\right|^2\right]
		I_0\left[\frac{\rho^2}{4}\left|a(t')\right|^2\right]
		dt'
	}.
\end{eqnarray}
%
Matrix elements that are not listed have values that are implied by the symmetry of the Fisher matrix. Note that the minus signs are correct but a little confusing: despite them, ${I}_{\gamma\gamma}, {I}_{\tau\tau} \geq 0$ and ${I}_{\gamma\tau} \leq 0$. The time integration limits $[-T, T]$ constitute a flat prior on arrival time, the time coincidence window between detectors.

Observe that
%
\begin{equation*}
	a(0) = 1,
	\qquad
	a'(0) = i \overline{\omega},
	\qquad
	a''(0) = -\overline{\omega^2}.
\end{equation*}
%
If we can show that the common factor approaches a delta function, $w(t; \rho) \rightarrow \delta(t)$ as $\rho \rightarrow \infty$, then the Fisher matrix for the autocorrelation likelihood approaches the Fisher matrix for the full GW data, \Eref{eq:fisher-matrix}, as $\rho \rightarrow \infty$. The Bessel functions asymptotically approach:
%
\begin{equation*}
	I_0(x), I_1(x) \rightarrow \frac{e^x}{\sqrt{2 \pi x}}
	\textrm{ as } x \rightarrow \infty.
\end{equation*}
%
For large $\rho$, the exponential dominates and we can write:
%
\begin{equation*}
	w(t; \rho) \rightarrow \frac{
		\displaystyle
		\exp\left[\frac{\rho^2}{2}|a(t)|^2\right]
	}{
		\displaystyle
		\int_{-T}^T \exp\left[\frac{\rho^2}{2}|a(t')|^2\right] dt'
	}
	\textrm{ as } \rho \rightarrow \infty.
\end{equation*}
%
The Taylor expansion of $|a(t)|^2$ is
%
\begin{equation*}
	|a(t)|^2 = 1 + \frac{1}{2} \left(\frac{\partial^2}{\partial t^2}|a(t)|^2 \Bigg|_{t=0}\right) t^2 + \mathcal{O}(t^4)
	= 1 - {\omega_\mathrm{rms}}^2 t^2 + \mathcal{O}(t^4).
\end{equation*}
%
Substituting, we find that $w(t; \rho)$ approaches a normalized Gaussian distribution:
%
\begin{equation*}
	w(t; \rho) \approx \frac{
		\displaystyle
		\exp\left[-\frac{1}{2} \rho^2 {\omega_\mathrm{rms}}^2 t^2\right]
	}{
		\displaystyle
		\int_{-T}^T \exp\left[-\frac{1}{2} \rho^2 {\omega_\mathrm{rms}}^2 (t')^2\right] dt'
	}.
\end{equation*}
%
And finally, because the Dirac delta function may be defined as the limit of a Gaussian, $w(t; \rho) \rightarrow \delta(t)$ as $\rho \rightarrow \infty$.

We can now write the Fisher matrix for the autocorrelation likelihood in a way that makes a comparison to the full signal model explicit. Define:
%
\begin{eqnarray*}
	\mathcal{I}_\gamma\gamma &=& \rho^2 \cdot \textproto{D}_{\gamma\gamma}(\rho) \\
	\mathcal{I}_\tau\tau &=& \rho^2 \overline{\omega^2} \cdot \textproto{D}_{\tau\tau}(\rho) \\
	\mathcal{I}_\gamma\tau &=& -\rho^2 \overline{\omega} \cdot \textproto{D}_{\gamma\tau}(\rho)
\end{eqnarray*}
%
Now, the $\textproto{D}_{ij}$ %
%
\marginpar{The Fish(er) factor. Go home, Leo.}%
%
contain the integrals from Equations~(\ref{eq:fisher-autocor-gamma-gamma}, \ref{eq:fisher-autocor-tau-tau}, \ref{eq:fisher-autocor-gamma-tau}) and encode the departure of the autocorrelation likelihood from the likelihood of the full data at low SNR. All of the $\textproto{D}_{ij}(\rho)$ are sigmoid-type functions that run from 0 at $\rho = 0$ and asymptotically approach 1 as $\rho \rightarrow \infty$. The transition SNR $\rho_\mathrm{crit}$ is largely the same for all three nontrivial matrix elements, and is determined by the time coincidence window $T$ and the signal bandwidth $\omega_\mathrm{rms}$.
%
\marginpar{The transition SNR is probably proportional to some power of $(\omega_\mathrm{rms} T)$.}

>>>>

Assuming circular orbits and no spin precession, we can write the \ac{GW} signal in each detector as a linear combination of two basis waveforms $h_0$ = $h$ and $h_{\pi/2}$. For nonprecessing systems, $h_0$ and $h_{\pi/2}$ are approximately ``in quadrature'' in the same sense as the sine and cosine functions, being nearly orthogonal and out of phase by ${\pi/2}$ at all frequencies. If $h_0$ and $h_{\pi/2}$ are Fourier transforms of real functions, then $h_0(\omega) = h_0^*(-\omega)$ and $h_{\pi/2}(\omega) = h_{\pi/2}^*(-\omega)$, and we can write (assuming an arbitrary phase convention)
%
\begin{equation}
	h_{\pi/2}(\omega) = h_0(\omega) \cdot
	\cases{
		-i & if $\omega \geq 0$ \\
		i & if $\omega < 0$
	}.
\end{equation}
%
Then, we can write the signal model in a way that isolates all dependence on the extrinsic parameters $\boldsymbol\theta_\mathrm{ex}$ into the coefficients and all dependence on the intrinsic parameters $\boldsymbol\theta_\mathrm{in}$ into the basis waveform, by taking the Fourier transform of Equation~(2.8) of \cite{PhysRevD.83.084002}:
%
\begin{equation}\label{eq:full-signal-model}
	h_i(\omega; \boldsymbol\theta) = \e^{-i \omega t_\oplus}
	\frac{D_{1,i}}{D_\mathrm{L}}
	\e^{2 i \phi_c}
	\left[
	\frac{1}{2} \left(1 + \cos^2 \iota\right) \Re \left\{z\right\} - i
	\left(\cos\iota\right) \Im z
	\right]
	h(\omega; \boldsymbol\theta_\mathrm{in})
\end{equation}
%
for $\omega \geq 0$, where
%
\begin{equation}
	z = e^{-2 i \psi} \left(
	F_{+,i}(\alpha, \delta, t_\oplus) +
	i F_{\times,i}(\alpha, \delta, t_\oplus)
	\right).
\end{equation}
%
The quantities $F_{+,i}$ and $F_{\times,i}$ are the dimensionless detector antenna factors, defined such that $0 \leq {F_{+,i}}^2 + {F_{\times,i}} \leq 1$. They depend on the orientation of detector $i$ as well as the sky location and sidereal time of the event, and are derived in~\cite{PhysRevD.63.042003}. The quantity $D_{1,i}$ is a fiducial distance at which detector $i$ would register SNR=1 for an optimally oriented binary (face\nobreakdashes-on, and in a direction perpendicular to the interferometer's arms),
%
\marginpar{I seem to have dropped a factor of 2 here...}%
%
\begin{equation}\label{eq:horizon}
D_{1,i} = 1 / \sigma_i, \qquad {\sigma_i}^2 = \int_0^\infty \frac{\left|h(\omega; \mathbf \theta)\right|^2}{S_i(\omega)} \,d\omega.
\end{equation}

@@

The Fisher information matrix for a measurement $x$ described by the unknown parameter vector $\boldsymbol{\theta}$ is
%
\begin{equation}\label{eq:general-fisher-matrix}
	\mathcal{I}_{jk} = \mathrm{E} \, \left[
		-\frac{\partial^2 \log
			\mathcal{L}(x_i ; \boldsymbol\theta)}
			{\partial \theta_j \theta_k}
	\middle| \boldsymbol\theta
	\right].
\end{equation}
%
In other words, it is the expectation value, condition on the true parameter values, of the Jacobian of the log likelihood. This equation involves double derivatives, but substantial simplification is possible when---as in this case---the likelihood is Gaussian:
%
\begin{equation}\label{eq:gaussian-fisher-matrix}
	\mathcal{I}_{jk} = \int_0^\infty \Re \left[
        \left(\frac{\partial h_i}{\partial \theta_j}\right)^*
        \left(\frac{\partial h_i}{\partial \theta_k}\right)
	\right] \frac{1}{S_i(\omega)} \, d\omega.
\end{equation}
%
This form is more useful because it involves only first derivatives, and of the signal $h (\omega)$ rather than the entire observation $x (\omega)$. In terms of the $k$th \ac{SNR}-weighted moment of angular frequency,
%
\begin{equation}\label{eq:angular-frequency-moments}
    {\overline{\omega^k}}_i =
        \left[ \int_0^\infty \frac{|h (\omega)|^2}{S_i(\omega)} \omega^k \, d\omega \right]
        \left[ \int_0^\infty \frac{|h (\omega)|^2}{S_i(\omega)} \, d\omega \right]^{-1},
\end{equation}
%
the Fisher matrix for the signal in the $i$th detector is
%
\begin{equation}
	\mathcal{I}_i = \left(
		\begin{array}{cc}
			\mathcal{I}_{\boldsymbol\theta_i,\boldsymbol\theta_i} &
			\mathcal{I}_{\boldsymbol\theta_i,\boldsymbol\theta_\mathrm{in}} \\
			{\mathcal{I}_{\boldsymbol\theta_i,\boldsymbol\theta_\mathrm{in}}}^\intercal &
			{\rho_i}^2 \mathcal{I}_{\boldsymbol\theta_\mathrm{in},\boldsymbol\theta_\mathrm{in}}
		\end{array}
	\right)
\end{equation}
%
where
%
\begin{equation}\label{eq:fisher-matrix}
	\mathcal{I}_{\boldsymbol\theta_i,\boldsymbol\theta_i} = \bordermatrix{
        ~ & \rho_i & \gamma_i & \tau_i \cr
        \rho_i & 1 & 0 & 0 \cr
        \gamma_i & 0 & {\rho_i}^2 & -{\rho_i}^2 {\overline{\omega}}_i \cr
        \tau_i & 0 & -{\rho_i}^2 {\overline{\omega}}_i & {\rho_i}^2 {\overline{\omega^2}}_i
    }.
\end{equation}
%
To lowest post\nobreakdashes-Newtonian order, the intrinsic parameters affect the phase evolution but not the amplitude evolution, so for BNS systems we can assume $\mathcal{I}_{\rho_i,\boldsymbol\theta_\mathrm{in}} \approx 0$.
%
\marginpar{Show this?}%
%
When we form the Fisher matrix for the whole network, if the detectors all have the same noise \acp{PSD}, $S_1(\omega) = S_1(\omega) = \cdots = S_n(\omega) \equiv S(\omega)$, then we can change variables from phases and times on arrival $\left\{\gamma_i, \tau_i\right\}_i$ to appropriate differences between them, in order to cancel out all off-diagonal terms between the intrinsic and extrinsic parameters. Because all existing ground-based GW detectors have similar bandpasses, we restrict all of our further attention to just the extrinsic part of the Fisher matrix, $\mathcal{I}_{\boldsymbol\theta_i,\boldsymbol\theta_i}$.

@@

First, observe that at the true parameter values, $\hat{\boldsymbol\theta}_i = \boldsymbol\theta_i$, the logarithms of \Eref{eq:autocor-likelihood} and \Eref{eq:gaussian-likelihood-spa} have the same Jacobian. This is because the derivatives of the autocorrelation function are
%
\begin{equation*}
    a^{(n)}(t) = i^n \overline{\omega^n};
\end{equation*}
%
for instance,
%
\begin{equation*}
    a(0) = 1,
    \qquad
    a'(0) = i \overline{\omega},
    \qquad
    a''(0) = -\overline{\omega^2}.
\end{equation*}

We can compute the Fisher matrix elements for the autocorrelation likelihood given by \Eref{eq:autocor-likelihood}, with detector subscript suppressed:
%
\begin{eqnarray}
	\nonumber
	\mathcal{I}_{\rho\rho} &=& 1 \\
	\nonumber
	\mathcal{I}_{\rho\gamma} &=& 0 \\
	\nonumber
	\mathcal{I}_{\rho\tau} &=& 0 \\
	\label{eq:fisher-autocor-gamma-gamma}
	\mathcal{I}_{\gamma\gamma} &=& \rho^2
		\int_{-T}^T \left|a(t)\right|^2 w(t; \rho) dt \\
	\label{eq:fisher-autocor-tau-tau}
	\mathcal{I}_{\tau\tau} &=& -\rho^2
		\int_{-T}^T \Re\left[a^*(t) a''(t)\right] w(t; \rho) dt \\
	\label{eq:fisher-autocor-gamma-tau}
	\mathcal{I}_{\gamma\tau} &=& -\rho^2
		\int_{-T}^T \Im\left[a^*(t) a'(t)\right] w(t; \rho) dt \\
	\nonumber\textrm{where} && \\
	w(t; \rho) &=& \frac{
		\displaystyle
		\exp\left[\frac{\rho^2}{4}\left|a(t)\right|^2\right]
		\left(
		I_0\left[\frac{\rho^2}{4}\left|a(t)\right|^2\right] +
		I_1\left[\frac{\rho^2}{4}\left|a(t)\right|^2\right]
		\right)
	}{
		\displaystyle
		2 \int_{-T}^T
		\exp\left[\frac{\rho^2}{4}\left|a(t')\right|^2\right]
		I_0\left[\frac{\rho^2}{4}\left|a(t')\right|^2\right]
		dt'
	}.
\end{eqnarray}
%
Matrix elements that are not listed have values that are implied by the symmetry of the Fisher matrix. Note that the minus signs are correct but a little confusing: despite them, ${I}_{\gamma\gamma}, {I}_{\tau\tau} \geq 0$ and ${I}_{\gamma\tau} \leq 0$. The time integration limits $[-T, T]$ constitute a flat prior on arrival time, the time coincidence window between detectors.

If we can show that the weighting function $w(t; \rho)$ approaches a Dirac delta function as $\rho \rightarrow \infty$, then the Fisher matrix for the autocorrelation likelihood approaches the Fisher matrix for the full GW data, \Eref{eq:fisher-matrix}, as $\rho \rightarrow \infty$. The Bessel functions asymptotically approach:
%
\begin{equation*}
	I_0(x), I_1(x) \rightarrow \frac{e^x}{\sqrt{2 \pi x}}
	\textrm{ as } x \rightarrow \infty.
\end{equation*}
%
For large $\rho$, the exponential dominates and we can write:
%
\begin{equation*}
	w(t; \rho) \rightarrow \frac{
		\displaystyle
		\exp\left[\frac{\rho^2}{2}|a(t)|^2\right]
	}{
		\displaystyle
		\int_{-T}^T \exp\left[\frac{\rho^2}{2}|a(t')|^2\right] dt'
	}
	\textrm{ as } \rho \rightarrow \infty.
\end{equation*}
%
The Taylor expansion of $|a(t)|^2$ is
%
\begin{equation*}
	|a(t)|^2 = 1 + \frac{1}{2} \left(\frac{\partial^2}{\partial t^2}|a(t)|^2 \Bigg|_{t=0}\right) t^2 + \mathcal{O}(t^4)
	= 1 - {\omega_\mathrm{rms}}^2 t^2 + \mathcal{O}(t^4).
\end{equation*}
%
Substituting, we find that $w(t; \rho)$ approaches a normalized Gaussian distribution:
%
\begin{equation*}
	w(t; \rho) \approx \frac{
		\displaystyle
		\exp\left[-\frac{1}{2} \rho^2 {\omega_\mathrm{rms}}^2 t^2\right]
	}{
		\displaystyle
		\int_{-T}^T \exp\left[-\frac{1}{2} \rho^2 {\omega_\mathrm{rms}}^2 (t')^2\right] dt'
	}.
\end{equation*}
%
And finally, because the Dirac delta function may be defined as the limit of a Gaussian, $w(t; \rho) \rightarrow \delta(t)$ as $\rho \rightarrow \infty$.

We can now write the Fisher matrix for the autocorrelation likelihood in a way that makes a comparison to the full signal model explicit. Define:
%
\begin{eqnarray*}
	\mathcal{I}_{\gamma\gamma} &=& \rho^2 \cdot \textproto{D}_{\gamma\gamma}(\rho) \\
	\mathcal{I}_{\tau\tau} &=& \rho^2 \overline{\omega^2} \cdot \textproto{D}_{\tau\tau}(\rho) \\
	\mathcal{I}_{\gamma\tau} &=& -\rho^2 \overline{\omega} \cdot \textproto{D}_{\gamma\tau}(\rho)
\end{eqnarray*}
%
Now, the $\textproto{D}_{ij}$ %
%
\marginpar{The Fish(er) factor. Go home, Leo.}%
%
contain the integrals from Equations~(\ref{eq:fisher-autocor-gamma-gamma}, \ref{eq:fisher-autocor-tau-tau}, \ref{eq:fisher-autocor-gamma-tau}) and encode the departure of the autocorrelation likelihood from the likelihood of the full data at low SNR. All of the $\textproto{D}_{ij}(\rho)$ are sigmoid-type functions that run from 0 at $\rho = 0$ and asymptotically approach 1 as $\rho \rightarrow \infty$. The transition SNR $\rho_\mathrm{crit}$ is largely the same for all three nontrivial matrix elements, and is determined by the time coincidence window $T$ and the signal bandwidth $\omega_\mathrm{rms}$.
%
\marginpar{The transition SNR is probably proportional to some power of $(\omega_\mathrm{rms} T)$.}
